\documentclass[a4paper, 11pt, twoside]{book}
\usepackage{sty/packages}

\newglossary[tlg]{team}{tlo}{tls}{Teams}
\makeglossaries
\input{team_gloss}


\makeatletter
\def\input@path{{sty/}}
\makeatother

\usepackage{mycolors}
\usepackage{definitions}
\usepackage{commands}

\title{Project documentation and wiki development for iGEM projects}
\date{}
\author{}

\begin{document}
\pagecolor{pgcolor}
\frontmatter
\maketitle

\tableofcontents
\newpage

\input{other/copyright}
\pagecolor{pgcolor}
% TODO: WIKIMEDIA als SVG Quelle angeben + https://freesvg.org/mitochondria

\renewcommand{\chapterdate}{30.06.2025}
\chapter{Introduction} \label{ch:introduction}
% TODO Science communication - Bigen dazu dass das für später wichtog ist weil man das im Job können muss um
% verstanden zu werden, aber auch um Grants zu bekommen etc
This guide is a comprehensive introduction to creating and managing an iGEM wiki from the absolute basics to the
technical documentation of a modern React-based template wiki designed specifically for iGEM teams and to both
seasonal project documentation for the competition as well as how to document for future teams from your university.  \\ \newline
It is organized into various sections that cover specific aspects of project management, collaboration, design, documentation, and technical implementation. \\ \newline
Throughout this guide, I will assume a successful activation of the team Wiki but will walk the reader through the fundamental aspects of setting up the Wiki, as well as providing a general overview of project documentation.
I will emphasize key elements that are essential for the Wiki team, such as effective documentation, clarity, and organizational strategies.
The coding section will specifically focus on React applications, explaining the basics and offering guidance on best practices and methods for creating a dynamic and user-friendly interface. \\ \newline
At the end of the guide, there will be an index list to help you easily find specific topics and navigate through the content more efficiently. \\ \newline
This guide also serves as documentation to the associated template wiki, which teams are free to use as a starting point.
It can be found at \url{https://github.com/liliana-sanfilippo/igem-wiki-guide}.
\paragraph{The Template Wiki} is a React-based, easily customizable template for iGEM wikis.
It is aimed at first-time teams with little experience as well as advanced iGEM teams.
The goal is to make it easier to get started with the technical implementation of your wiki without having to compromise on functionality or flexibility. \\ \newline
The template is currently developed further, including some independent packages.
It offers a modern, modular code base that can be easily adapted and extended.
The aim is better usability and maintainability compared to the example wiki provided by iGEM through additional functions, including components designed to work with the template specifically. \\ \newline
It is a first version and I will be working on improving it, so any feedback or ideas can be sent to liliana.sanfilippo@uni-bielefeld.de or raised as issues on GitHub. \\ \newline
Documentation for other tools or packages by myself is not included, but wil be linked. \\ \newline
While updating the guide, some already finished sections will be re-added and the following aspects will be added:
\begin{itemize}
    \item An in-depth explanation on how to implement a citation React component
    \item Setting Global Variables in React
    %\item Creating HTML Code with Python
    \item Wiki Thaw
    \item Utilizing Bootstrap
    \item FAQ
    \item Merge Conflicts
    \item Utilizing ChatGPT
    \item Where can I get help?
    \item Definitions of terms such as CSS path, CSS selector
    \item Errors and Troubleshooting
    \item html link targets
    \item Mobile responsiveness
    \item Further Collaborations and Considerations with other subteams (e.g.\ Sponsoring and logos)
    \item Scrolling animations
    \item Possibly education and HP documentation frameworks
    \item Appendix for first time teams with basic, but possibly unknown information and considerations
    % TODO Parsable with schema.org
    % TODO Wiki lead und organisation
    % TODO Doc breaker iGEM Guelph
    % https://stackoverflow.com/questions/16230959/what-does-top-in-the-hyperlink-target-do
\end{itemize}
As well as additional images outlining the instructions and examples given.
\newpage



\mainmatter
\pagecolor{pgcolor}

\part{Documentation}
\chapter{Setting up the documentation and organisation}\label{ch:setting-up-the-documentation-and-organisation}
Creating well-structured documentation\index{Documentation} is essential for effective communication and information retention.
It is also very helpful for the next team at your university to have good internal documentation of contacts and
resources.

We will start with the internal documentation and continue with the project documentation for the competition.
Please adapt the suggestions to your needs.
% DONE (can be expanded)
%\chapter{Documentation} \label{ch:docu}
\input{chapters/001internalorga}
\input{chapters/03documentation}
\newpage
%
\part{Wiki preparation and planning}\label{part:wiki-preparation-and-planning}


\chapter{Design} \label{ch:design}
\input{chapters/02design}
% TODO Explizit anbringen dass Epunks das gesagt hat und die in Attributions dazu packen
\newpage
%
\chapter{User-friendliness and usability - Under construction}\label{ch:user-friendliness-and-usability}
% TODO
\input{chapters/04usability}
\newpage
%
\chapter{Website and page structures} \label{ch:webstructure}
\input{chapters/06webstructure}
\newpage
% DONE
\chapter{Getting started with the wiki} \label{ch:started}
\input{chapters/01gettingstarted}
\newpage
% DONE File structure
\chapter{File structure} \label{ch:structure}
\input{chapters/05structure}
\newpage
%
\chapter{Media  - Pending}\label{ch:media}
Upload pending. % TODO
%\subfile{sections/media}
\newpage
%
%
\chapter{Wiki guide for team - Pending} \label{ch:guide}
Upload pending. % TODO
%\subfile{sections/guide}
\newpage

\part{Wiki development}
\chapter{Coding prequisites} \label{ch:prequisites}
\input{chapters/08prequisites}
% TODO \section*{For Plain HTML Projects} from cod.tex nicht drin
% TODO Bildanleitungen ergänzen
\newpage
%
\chapter{General Coding}  \label{ch:coding}
% TODO Empfehlung für Kalender als Übung
\input{chapters/09generalcoding}
\newpage
%
\chapter{React} \label{ch:react}

\input{chapters/10react}
% HTML vs JSX
% TODO \subfile{sections/bibtexparser}
% TODO Creating efficient reusable components for the team to work with
\newpage
%
\chapter{Additional tools - Under construction} \label{ch:addtools}
% Upload pending. % TODO 
\input{chapters/11additionaltools}
\newpage
%
\chapter{Troubleshooting - Pending} \label{ch:troubleshooting}
Upload pending. % TODO 
%\subfile{sections/troubleshooting}
\newpage
%

\chapter{Accessibility - Under Construction} \label{ch:accessibility}
Upload pending. % TODO
\input{chapters/16accessibility}

\chapter{Scientific writing - Under Construction} \label{ch:scientificwriting}
Upload pending. % TODO
\input{chapters/17scientificwriting}

\chapter{Other frameworks and systems - Under Construction} \label{ch:othersystems}
Upload pending. % TODO
\input{chapters/18othersystems}

\chapter{The Wiki Freeze - Under construction}  \label{ch:freeze}
%Upload pending. % TODO
\input{chapters/14wikifreeze}
\newpage
%

\part{Special prizes}\label{part:special-prizes}
\input{chapters/specialprizes}

\chapter{Best Wiki - Pending} \label{ch:bestwiki}
%\subfile{sections/bestwiki}
Upload pending. % TODO
\newpage

\part{After the Jamboree}
\chapter{The Wiki Thaw - Pending} \label{ch:thaw}
Upload pending. % TODO 
%\subfile{sections/thaw}
\newpage
% Todo turning over the documentation to the new team
%
%\chapter{Code Snippets and React Components} \label{ch:appendix}
%Upload pending. % TODO
%\subfile{sections/appendix}
%\newpage

\part{Appendix}
\backmatter
\pagenumbering{Roman}
\pagecolor{pgcolor}

\chapter{Documentation framework examples}\label{ch:documentation-framework-examples}
\input{other/frameworks}

\chapter{Component Examples}
\input{other/components}

\chapter{Notable Design Examples}
\input{other/design}

\chapter{Sources}
Test:
\typeout{TYPE=\glsentrytype{wageningen22}}
\addcontentsline{toc}{section}{Teams mentioned}
\glsaddall[types={team}]
\printglossary[type=team, title=Teams]

\section{Associated software} \label{ch:associated-software}
\input{other/associated-software}

\section{Attributions} \label{ch:attributions}
\input{other/attributions}
%
%\chapter{HTML Cheat Sheet} \label{ch:htmlcheatsheet}
%Upload pending. % TODO
%\subfile{sections/htmlcheatsheet}
%\newpage

%\chapter{Sources}\label{ch:sources}
%\printbibliography

\end{document}